Software Citation Principles

### 2016-07-26 sc-principles/software-citation-principles.tex
added 2nd transitive credit ref to text

The principles in this document should guide further development of software citation
mechanisms and systems, and the reader should be able to look at any particular example
of software citation and see if it meets the principles.
While we strive to offer practical guidelines that acknowledge the current
incentive system of academic citation, a more modern system of assigning credit
is sorely needed. It is not that academic software needs a separate credit
system from that of academic papers, but that the need for credit for
research software underscores the need to overhaul the system of credit for
all research products. One possible solution for a more complete description of the
citations and associated credit is discussed in Katz~\cite{transitive_credit_original}.

>>>>

The principles in this document should guide further development of software citation
mechanisms and systems, and the reader should be able to look at any particular example
of software citation and see if it meets the principles.
While we strive to offer practical guidelines that acknowledge the current
incentive system of academic citation, a more modern system of assigning credit
is sorely needed. It is not that academic software needs a separate credit
system from that of academic papers, but that the need for credit for
research software underscores the need to overhaul the system of credit for
all research products. One possible solution for a more complete description of the
citations and associated credit is the transitive credit proposed by
Katz and Smith~\cite{transitive_credit_original,transitive_credit_json-ld}.
